\documentclass[11pt]{article}
\usepackage[document]{ragged2e}
\usepackage[letterpaper, margin=0.5in]{geometry}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{booktabs} % fancy lines for tables
\usepackage{caption}
\usepackage{enumitem} % customize item labels
\usepackage{endnotes}
\usepackage{float}    % force figure position to match source
\usepackage{fontspec}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{pgfplots} % graph functions
\usepackage{setspace}
\usepackage{shellesc}
\usepackage{tabularx} % arbitrary table column widths
\usepackage{tikz}     % general drawing
\usepackage{titlesec}  % control heading sizes and spacing

\input{config.tex}

\begin{document}

\begin{center}
\LARGE\bfseries Matthew McCall \\
\normalsize\normalfont Branford, CT \,\textbullet\, m-mccall@outlook.com \,\textbullet\, www.linkedin.com/in/96d9
\end{center}

\textbf{Skills:} C++, GNU/Linux, Git, MATLAB, KiCad, SPICE, SystemVerilog, SolidWorks, LaTeX, MS Word, Excel, PowerPoint

\section*{Education}
\company{Rensselaer Polytechnic Institute}{Troy, NY}{}
Bachelor's in Computer Science and Computer Systems Engineering \hfill \textbf{May 2026} \\
\textbf{Relevant Coursework:} Computer Hardware Design, Microprocessor Systems, Space Vehicle Design

\section*{Work Experience}

\company{Health Innovation Incubator}{Watervliet, NY}{March 2026 -- Present}
\textit{Intern}
\begin{itemize}
	\item Working on a communication device for hospitalized children with disabilities to express non-urgent needs (e.g., food, water, medication refills) to nurses.
	\item Contributing to the design of the modular, customizable communication device platform so can be tailored to each child’s abilities.
	\item Contributing to the design of a scalable wireless protocol capable of supporting hundreds of communication devices within a hospital environment.
\end{itemize}

\company{HarcoSemco}{Branford, CT}{May 2025 -- August 2025}
\textit{Engineering and Quality Intern}
\begin{itemize}
    \item Led the development of a Bluetooth-based asset tracking system for an aerospace manufacturing environment.
    \item Designed the gateway-tag network architecture, selected hardware components, and developed software in C++, Java, and Kotlin, deploying a system capable of tracking assets across a 12,000 sq. ft. facility with 8-foot positional accuracy.
    \item Engineered C++ software for toxic gas detection using Bosch sensors, transmitting environmental data via Bluetooth. Developed a React TypeScript dashboard using Web Bluetooth to display real-time sensor readings, ensuring compliance with aerospace safety and quality protocols.
\end{itemize}

\company{Scientific Computation Research Center}{Troy, NY}{August 2022 -- Present}
\textit{Research Assistant}
\begin{itemize}
    \item Implemented a GPU memory pool to reduce runtime by 30\% for Omega\_h, a C++ library for mesh adaptivity.
    \item Developed a C++ algorithm to compute the nearest simplex to a point in an n-dimensional mesh for PCMS, a mesh coupling library.
    \item Authored a scientific paper in \LaTeX\,and presented the work at the Spring 2024 RPI Undergraduate Research Symposium.
\end{itemize}

\company{Mercer X Lab}{Troy, NY}{January 2025 -- May 2025}
\textit{Lab Assistant}
\begin{itemize}
	\item Guided students in safety best practices, circuit design, soldering, and proper lab equipment usage.
\end{itemize}

\section*{Project Experience}

\subsection*{Open Algebra Software for Inferring Solutions (OASIS)}
\begin{itemize}
	\item Currently leading the development of the OASIS project, an open-source C++ library for computer algebra and symbolic manipulation, coordinating contributors and managing development workflows using GitHub Issues, Projects, and Pull Requests. Implemented GitHub Actions CI/CD pipelines to automate building and unit testing, improving code reliability and streamlining the development process.
\end{itemize}

\subsection*{Eye Robot}
\begin{itemize}
    \item Eye Robot is a navigation robot designed to assist visually impaired users. Collaborated on a team to develop C\# and C++ software that constructs a 3D model of the environment using LiDAR and transmits navigation
    commands to an onboard ESP32 microcontroller.
\end{itemize}

\subsection*{Helpful Assessment Readiness Platform}
\begin{itemize}
    \item Won Best AI Hack and Best Use of DigitalOcean Gradient AI at HackRPI 2025 by developing a mock interview platform that uses AI agents to simulate interviewer personas and provide automated feedback to users.
\end{itemize}
\end{document}
